---
title: "marshall-fire-damage"
author: "Maxwell C. Cook"
date: "1/11/2022"
output: html_document
---

```{r setup, include=F, warning=F}
knitr::opts_chunk$set(echo = TRUE)
source("setup.R")
```

## Marshall Fire, CO (2021): Residential Damage Assessment

With 1,084 home destroyed, the Marshall Fire is Colorado's most destructive wildfire disaster and in the top 15 most destructive wildfires in the western United States since 1999. 

```{r}
glimpse(ztrax.res)
```

## Location and Proportion of Homes Damaged and Destroyed

```{r pressure, echo=FALSE, fig.height=5, fig.width=6.5}
N <- dim(ztrax.res)[1]
grob <- grobTree(
   textGrob("*Based on available ZTRAX data \n(90% of total homes destroyed)*", 
            x=0.05,  y=0.05, hjust=0, gp=gpar(col="grey20", fontsize=8, fontface="italic")))
# Calculate proportion destroyed, damaged
# Map
p1 <- ggplot() +
  geom_sf(data=ztrax.res.hull, aes(color=DAMAGE), size=0.8, shape=3) +
  scale_color_manual(values = c("#fecc5c", "#bd0026", "#c2e699")) +
  geom_sf(data=evt, fill=NA, color="grey10") +
  labs(title="Marshall Fire, CO (2021) Damage Assessment",
       caption="Data Sources:\nBoulder County Sheriff's Office,\nZillow Transaction and Assessment Database (ZTRAX),\nNIFC Current Fire Perimeters",
       color="Status") +
  annotation_custom(grob) +
  theme_void() +
  theme(plot.title = element_text(size = 12), legend.position=c(0.1, 0.8),
        plot.caption = element_text(size=7))
p1
ggsave(p1, file = "../../figures/MarshallFire_DmgAssess_Map.png",
       width=6.5, height=5, dpi = 450) # adjust dpi accordingly
```

## Multinomial (Categorical) Regression

```{r fig.height=3.25, fig.width=3.5}
# run a simple model
p2 <- ztrax.res.evt %>%
  ggplot(aes(x='',fill=DAMAGE)) +
  geom_bar(aes(y = (..count..)/sum(..count..))) + 
  scale_y_continuous(labels=scales::percent) +
  scale_fill_manual(values = c("#fecc5c", "#bd0026", "#c2e699")) +
  geom_text(aes(label = ..count..), stat='count', position='fill', vjust=1.1, size=3) +
  labs(x="", fill="", y="% of Homes in Perim.",
       caption="*Based on available ZTRAX Data (90% of total)*") +
  theme_minimal() +
  theme(plot.caption = element_text(size=7))
p2
ggsave(p2, file = "../../figures/MarshallFire_DmgAssess_StatusPerc.png",
       width=3.5, height=3.25, dpi = 300) # adjust dpi accordingly
```

# Year Built

```{r fig.width=5, fig.height=3}
# Density plot
ggplot(data=ztrax.res.evt, aes(x=YearBuilt)) +
  geom_density(stat='count') +
  theme_minimal()
# By destruction
ggplot(data=ztrax.res.evt, aes(x=YearBuilt, fill=DAMAGE)) +
  geom_bar(stat='count', position='stack') +
  scale_fill_manual(values = c("#fecc5c", "#bd0026", "#c2e699")) +
  theme_minimal()
```

# Roof Cover

```{r}
summary(factor(ztrax.res.evt$RoofCoverStndCode))
```

Testing missingness.

```{r}
print("Missingness: ...")
paste("Year built: ",dim(ztrax.res%>%filter(is.na(YearBuilt)))[1], sep="")
paste("Effective year built: ",dim(ztrax.res%>%filter(is.na(EffectiveYearBuilt)))[1], sep="")
paste("Building area (sqft): ",dim(ztrax.res%>%filter(is.na(BuildingAreaSqFt)))[1], sep="")
paste("Lot size (sqft): ",dim(ztrax.res%>%filter(is.na(LotSizeSquareFeet)))[1], sep="")
paste("Tax amount: ",dim(ztrax.res%>%filter(is.na(TaxAmount)))[1], sep="")
paste("No. of buildings: ",dim(ztrax.res%>%filter(is.na(NoOfBuildings)))[1], sep="")
paste("Total assessed value: ",dim(ztrax.res%>%filter(is.na(TotalAssessedValue)))[1], sep="")
paste("Lot assessed value: ",dim(ztrax.res%>%filter(is.na(LandAssessedValue)))[1], sep="")
paste("Improvement value: ",dim(ztrax.res%>%filter(is.na(ImprovementAssessedValue)))[1], sep="")
paste("Wall material: ",dim(ztrax.res%>%filter(is.na(ExteriorWallStndCode)))[1], sep="")
paste("Roof cover: ",dim(ztrax.res%>%filter(is.na(RoofCoverStndCode)))[1], sep="")
paste("Quality code: ",dim(ztrax.res%>%filter(is.na(BuildingQualityStndCode)))[1], sep="")
paste("LU code: ",dim(ztrax.res%>%filter(is.na(PropertyLandUseStndCode)))[1], sep="")
paste("Heating type: ",dim(ztrax.res%>%filter(is.na(HeatingTypeorSystemStndCode)))[1], sep="")
paste("AC type: ",dim(ztrax.res%>%filter(is.na(AirConditioningTypeorSystemStndCode)))[1], sep="")
```

## Binomial GLM

```{r}
# tidy up!
mod.df <- ztrax.res.evt %>% 
  mutate(DESTROY = if_else(DAMAGE=="Destroyed", 1, 0),
         BuildingAreaSqFt = as.numeric(BuildingAreaSqFt),
         RoofCoverStndCode = as.factor(RoofCoverStndCode),
         RoofCoverDummy = as.factor(if_else(RoofCoverStndCode!="OT", "OTHER",  "OT")),
         ExteriorWallStndCode = as.factor(ExteriorWallStndCode),
         ExtWallDummy = as.factor(if_else(ExteriorWallStndCode!="OT", "OTHER", "OT")),
         BuildingQualityStndCode = as.factor(BuildingQualityStndCode),
         QualityDummy = as.factor(if_else(BuildingQualityStndCode!="C", "OTHER", "C")),
         PropertyLandUseStndCode = as.factor(PropertyLandUseStndCode))
mod.df <- within(mod.df, RoofCoverDummy <- relevel(RoofCoverDummy, ref = "OTHER"))
mod.df <- within(mod.df, ExtWallDummy <- relevel(ExtWallDummy, ref = "OTHER"))
mod.df <- within(mod.df, QualityDummy <- relevel(QualityDummy, ref = "OTHER"))

# Set up the binomial GLM
m1f <- glm(
  DESTROY ~ YearBuilt + log(BuildingAreaSqFt) + log(LotSizeSquareFeet) + 
    RoofCoverDummy + ExtWallDummy + QualityDummy + NoOfBuildings, 
  family = binomial(link = "logit"), data = mod.df)
summary(m1f)
```

## Bayes GLM

Intercept only.

```{r include=F}
setwd('../../')
m1b <- brm(
  DESTROY ~ 1,
  family = bernoulli(link = "logit"), data = mod.df, 
  iter = 2000, warmup = 1000, cores = 4, chains = 4,
  backend = "cmdstanr", threads = threading(4),
  control = list(adapt_delta = 0.99, max_treedepth=15), 
  sample_prior = TRUE, save_pars = save_pars(all=TRUE),
  seed = 123, file = paste(getwd(), "fits/m1b.Rds", sep="/")
)
```

Model summary.

```{r}
summary(m1b)
```

Check for non-convergence in the chains. 

```{r fig.height=2.5, fig.width=4}
mcmc_plot(m1b, type = "trace")
```

Check for autocorrelation.

```{r fig.height=4, fig.width=6}
mcmc_plot(m1b, type = "acf_bar")
```

Point estimates and associated uncertainty levels.

```{r fig.height=2, fig.width=3}
stanplot(m1b, type = "areas", prob = 0.95)
```

Update model with exterior wall material.

```{r include=F}
m1.1b <- update(
  m1b, formula. = bf(DESTROY ~ 1 + ExtWallDummy), newdata = mod.df, recompile = T
)
```

```{r}
summary(m1.1b)
```

Exponentiated fixed effects.

```{r}
exp(fixef(m1.1b)[,-2])
```

```{r fig.height=3, fig.width=2.5}
conditional_effects(m1.1b)
```


## Ordinal / Categorical Bayes Model

Check on the default priors.

```{r}
get_prior(data = ztrax.res.evt, family = categorical(link = logit, refcat = "Intact"), DAMAGE ~ 1)
```

Fit the intercept model.

```{r include=F, warning=F}
setwd("C:/Users/mccoo/OneDrive/mcook/earth-lab/marshall-fire/")
m1.1 <- brm(
  DAMAGE ~ 1, family = categorical(link = logit, refcat = "Intact"),
  data = ztrax.dmg,
  prior = c(prior(normal(0, 1), class = Intercept, dpar = muDestroyed),
            prior(normal(0, 1), class = Intercept, dpar = muDamaged)),
  iter = 2000, warmup = 1000, cores = 4, chains = 4,
  backend = "cmdstanr", threads = threading(4),
  control = list(adapt_delta = 0.99, max_treedepth=15), 
  sample_prior = TRUE, save_pars = save_pars(all=TRUE),
  seed = 1)
```

```{r}
summary(m1.1)
```

```{r}
fitted(m1.1)[1, , ] %>% 
  round(digits = 2) %>% 
  t()
```

```{r}

```

```{r}

```

